

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Long Professional Curriculum Vitae
% LaTeX Template
% Version 1.1 (9/12/12)
%
% This template has been downloaded from:
% http://www.latextemplates.com
%
% Original author:
% Rensselaer Polytechnic Institute (http://www.rpi.edu/dept/arc/training/latex/resumes/)
%
% Important note:
% This template requires the res.cls file to be in the same directory as the
% .tex file. The res.cls file provides the resume style used for structuring the
% document.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass[10pt]{res} % Use the res.cls style, the font size can be changed to 11pt or 12pt here

\usepackage{helvet} % Default font is the helvetica postscript font
\usepackage{hyperref}
%\usepackage{newcent} % To change the default font to the new century schoolbook postscript font uncomment this line and comment the one above


\usepackage{lipsum} % demo only

\usepackage{marvosym} % For cool symbols.


\usepackage{paracol}
\usepackage{multicol}

\begin{document}
	%----------------------------------------------------------------------------------------
	%	NAME AND ADDRESS SECTION
	%----------------------------------------------------------------------------------------
	
	%----------------------------------------------------------------------------------------
	%	YOUR NAME AND ADDRESS(ES) SECTION
	%----------------------------------------------------------------------------------------
	\name{\bf \Large{Shotaro N. Nakamura} \\ Last updated: \today  \\}
	% If you don't want one of the addresses, simply remove all the text in the first or second \address{} bracket
	\address{Federal Trade Commission \\ 600 Pennsylvania Ave NW \\ Washington, DC 20580}
	\hfill 
	\address{ \hfill {\href{mailto:shotaro.n.nakamura@gmail.com}{shotaro.n.nakamura@gmail.com} } \\  \hfill {\it Mobile:} +1 603-276-8129 \\  \hfill \href{https://shotaro-n-nakamura.github.io/}{https://shotaro-n-nakamura.github.io/}}
	
	%----------------------------------------------------------------------------------------
	
	\begin{resume}
		
		\section{Employment}
		Economist, Bureau of Economics, Federal Trade Commission  \hfill 2023-- 
		\vspace{-\baselineskip} 
		\section{Research Fields}
		Primary Fields: Development,  Energy and Environment\\
		Secondary Fields: Industrial Organization, Labor
		%----------------------------------------------------------------------------------------
		%	EDUCATION SECTION
		%----------------------------------------------------------------------------------------
		\section{Education}
		{\sl Ph.D.,} Economics, University of California, Davis  \hfill 2023 \\
		\hspace*{6mm} Visiting Ph.D. student, University of Copenhagen \hfill 2023 \\
		{\sl Master of Science,} Economics, London School of Economics and Political Science \hfill 2016 \\
		{\sl Bachelor of Arts,} Economics, Dartmouth College \hfill 2013 \\
		\vspace{-\baselineskip} 
		\vspace{-\baselineskip} 
		%----------------------------------------------------------------------------------------
		%	Teaching Experience
		%----------------------------------------------------------------------------------------
		\section{Teaching Experience} 
		Teaching Assistant, UC Davis  \hfill 2020-2021 \\
		\hspace*{6mm} Energy Economics, undergraduate \\
		\hspace*{6mm} Development Economics, undergraduate \\
		\hspace*{6mm} Industrial Organization, undergraduate  
		%Teaching Assistant, Economics 046: Topics in Finance, Dartmouth College \hfill Spring 2013\\
		%Japanese Language Drill Instructor, Japanese 001-003, Dartmouth College \hfill Fall 2010, Spring 2012 \\
		
		%----------------------------------------------------------------------------------------
		%	Term Papers and Research Projects
		%---------------------------------------------------------------------------------------- 
		\section{Working Papers}
		\hangindent=0.7cm ``{\href{https://shotaro-n-nakamura.github.io/img/Nakamura_JMP_Latest.pdf}{Distributional and productivity implications of regulating casual Labor: Evidence from ridesharing in Indonesia}}'' (with Rizki Siregar)
		
		\hangindent=0.7cm ``{Spillovers under Information and Search Frictions: Experimental Evidence from an Online Platform in Pakistan}'' (with Syed Ali Hasanain and Adeel Tariq) 
		
		\hangindent=0.7cm ``{Beliefs, signal quality, and information sources: Experimental evidence on air quality in Pakistan}'' (with Isra Imtiaz, Sanval Nasim, and Arman Rezaee)
		\vspace{-\baselineskip} 
		\section{Ongoing Projects}
		\hangindent=0.7cm ``{Transaction costs in adapting to air pollution: Experimental evidence from California}'' (with Collin Weigel)
		
		\hangindent=0.7cm ``{Distributional consequences of pre-paid electricity metering: Evidence from Dhaka}'' (with Debasish Das)
		
		\section{Presentations}
		\hangindent=0.7cm 2024 (including scheduled):  AERE session at Western Economic Association conference, Society of Government Economists Annual Conference, Pacific Conference for Development Economics (PacDev), AERE session at Eastern Economic Association conference, Japan Fair Trade Commission, Hitotsubashi University
		
		\hangindent=0.7cm 2023: World Bank DIME-KDI Development Impact Conference, The Heartland Environmental and Resource Economics Workshop, International Growth Centre, EEA-ESEM Barcelona 2023, Universitas Indonesia, National Team for the Acceleration of Poverty Reduction of the Indonesian Government (TNP2K), Nordic Conference in Development Economics (NCDE), University of Copenhagen, JADE/CEPR/TIME/CIRJE Development Economics Conference, Pacific Conference for Development Economics (PacDev), J-PAL MENA, Institut Mines-T\'{e}l\'{e}com, Federal Trade Commission
		
		\hangindent=0.7cm 2022: Yale Research Initiative on Innovation and Scale (Y-RISE) Conference, North East Universities Development Consortium (NEUDC), Conference on Digital Experimentation (CODE@MIT), Tokyo Labor Economics Workshop, Conference on Applied Development Economic at the Lahore School of Economics, Advances with Field Experiments
		\vspace{-\baselineskip} 
		%----------------------------------------------------------------------------------------
		%	Awards and Honors
		%----------------------------------------------------------------------------------------
		\section{Grants} 
		\hangindent=0.7cm  Shotaro Nakamura (PI), Matthew Gibson, Fatiq Nadeem, Sanval Nasim, and Arman Rezaee (Co-PIs). \textit{Belief Formation, Signal Quality, and Information Sources: Experimental Evidence on Air Quality from Pakistan}, 2022. International Growth Centre (IGC) PAK-22039. GBP 20,000. 
		
		\hangindent=0.7cm  Sanval Nasim (PI), Matthew Gibson, Shotaro Nakamura, and Arman Rezaee (Co-PIs). \textit{Belief Formation, Signal Quality, and Information Sources: Experimental Evidence on Air Quality from Pakistan}, 2021. International Growth Centre (IGC) PAK-21105. GBP 15,000. 
		
		\hangindent=0.7cm Girija Bahety, Castro Gichuki, and Shotaro Nakamura \textit{Do Community Currencies Induce ``Social'' Transactions and Enterprise Development?}, 2021. Private Enterprise Development in Low-Income Countries (PEDL). GBP 4,000. 
		
		\hangindent=0.7cm  Travel and Research Grants, Department of Economics, UC Davis,  \hfill 2018, 2021, 2022
	
		
		\section{Refereeing}
		Journal of Environmental Economics and Management
		\vspace{-\baselineskip} 
		\section{Additional Research Experiences}
		Research Assistant, Prof. Arman Rezaee, UC Davis \hfill 2018-2019 \\
		Research Assistant, Profs. Erich Muehlegger and David Rapson, UC Davis \hfill 2018-2019 \\
		Research Assistant (full-time pre-doc), Prof. Nava Ashraf, HBS and LSE \hfill 2014-2015, 2016-2017 \\
		Research Analyst, Harvard Graduate School of Education  \hfill  2013-2014 \\
		Research Assistant, Profs. Bruce Sacerdote and Sandip Sukhtankar, Dartmouth College \hfill 2010-2013 \\
		\vspace{-\baselineskip} 
		\vspace{-\baselineskip} 
		%----------------------------------------------------------------------------------------
		%	Awards and Honors
		%----------------------------------------------------------------------------------------
		\section{Awards and Honors} 
		Bilinski Educational Foundation Dissertation Writing Fellowship, UC Davis   \hfill 2022-2023  \\
		Dean's Distinguished Graduate Fellowship, UC Davis \hfill 2017-2022  \\
		Dean's Summer Graduate Fellowship, UC Davis \hfill 2020 \\
		Departmental Honors, Economics, Dartmouth College \hfill 2013 \\
		\vspace{-\baselineskip} 
		\vspace{-\baselineskip} 
		%----------------------------------------------------------------------------------------
		%	COMPUTER SKILLS SECTION
		%----------------------------------------------------------------------------------------
		\section{Software and Languages}
		Stata, R, \LaTeX, SQL \\
		English (fluent) Japanese (native), French (intermediate), Portuguese (intermediate)
		
		%----------------------------------------------------------------------------------------
		% References
		%----------------------------------------------------------------------------------------

		
		\section{References}
		\begin{multicols}{2}
			
			Prof. Arman Rezaee \\
			University of California, Davis \\
			\href{mailto:}{abrezaee@ucdavis.edu}
			
			
			\vfill\columnbreak
			
			Prof. David Rapson  \\
			University of California, Davis \\
			\href{mailto:}{dsrapson@ucdavis.edu}
			
		\end{multicols}
		
		Prof. Giovanni Peri  \\
		University of California, Davis \\
		\href{mailto:}{gperi@ucdavis.edu }
		
		
		%----------------------------------------------------------------------------------------
		
	\end{resume} 
\end{document}