
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Long Professional Curriculum Vitae
% LaTeX Template
% Version 1.1 (9/12/12)
%
% This template has been downloaded from:
% http://www.latextemplates.com
%
% Original author:
% Rensselaer Polytechnic Institute (http://www.rpi.edu/dept/arc/training/latex/resumes/)
%
% Important note:
% This template requires the res.cls file to be in the same directory as the
% .tex file. The res.cls file provides the resume style used for structuring the
% document.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass[10pt]{res} % Use the res.cls style, the font size can be changed to 11pt or 12pt here

\usepackage{helvet} % Default font is the helvetica postscript font
\usepackage{hyperref}
%\usepackage{newcent} % To change the default font to the new century schoolbook postscript font uncomment this line and comment the one above


\usepackage{lipsum} % demo only

\usepackage{marvosym} % For cool symbols.


\usepackage{paracol}
\usepackage{multicol}

\begin{document}
%----------------------------------------------------------------------------------------
%	NAME AND ADDRESS SECTION
%----------------------------------------------------------------------------------------

%----------------------------------------------------------------------------------------
%	YOUR NAME AND ADDRESS(ES) SECTION
%----------------------------------------------------------------------------------------

% If you don't want one of the addresses, simply remove all the text in the first or second \address{} bracket
\address{{\bf \Large{Shotaro N. Nakamura}} \\
	 1118 Social Sciences and Humanities \\  Davis, CA, USA \\ 95616}

\address{ \\ {\it Email}: {\href{mailto:snnakamura@ucdavis.edu}{snnakamura@ucdavis.edu} } \\ {\it Phone:} +1 603-276-8129 \\ {\it Website}: \href{https://shotaro-n-nakamura.github.io/}{https://shotaro-n-nakamura.github.io/}}

%----------------------------------------------------------------------------------------

\begin{resume}


%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------
\section{Education}
{\sl Ph.D.,} Economics, University of California, Davis  \hfill June, 2023 (anticipated) \\
{\sl Master of Science,} Economics, London School of Economics and Political Science \hfill 2016 \\
{\sl Bachelor of Arts,} Economics, Dartmouth College \hfill 2013 \\


 \section{Teaching and Research Fields}
 Primary Field: Development\\
 Secondary Fields: Energy and Environment, Public, Labor %----------------------------------------------------------------------------------------
 %	Teaching Experience
 %----------------------------------------------------------------------------------------
\section{Teaching Experience} 
Teaching Assistant, UC Davis  \hfill 2020-2021 \\
\hspace*{6mm} Energy Economics, undergraduate \\
\hspace*{6mm} Development Economics, undergraduate \\
\hspace*{6mm} Industrial Organization, undergraduate  \\
%Teaching Assistant, Economics 046: Topics in Finance, Dartmouth College \hfill Spring 2013\\
%Japanese Language Drill Instructor, Japanese 001-003, Dartmouth College \hfill Fall 2010, Spring 2012 \\

%----------------------------------------------------------------------------------------
%	Term Papers and Research Projects
%---------------------------------------------------------------------------------------- 
\section{Working Papers}
\hangindent=0.7cm Shotaro Nakamura (\textbf{Job Market Paper}) and Rizki Siregar \textit{Distributional and Productivity Implications of Regulating Casual Labor: Evidence from Ridesharing in Indonesia}. 

\hangindent=0.7cm Shotaro Nakamura, Syed Ali Hasanain and Adeel Tariq. \textit{Spillovers under Information and Search Frictions: Experimental Evidence from an Online Platform in Pakistan}. 

\section{Ongoing Projects}
\hangindent=0.7cm Matthew Gibson, Shotaro Nakamura, Sanval Nasim, and Arman Rezaee. \textit{Belief Formation, Signal Quality, and Information Sources: Experimental Evidence on Air Quality from Pakistan} (Fieldwork and intervention ongoing). 

\hangindent=0.7cm Collin Weigel and Shotaro Nakamura \textit{Transaction costs in adapting to air pollution: Experimental evidence in California}  (Funded and in the design phase). 
%\hangindent=0.7cm Hern\'{a}n Bejarano, Pedro Hancevic, Shotaro Nakamura, Hector Nu\~{n}ez, David Rapson, Juan Rosell\'{o}n. \textit{Energy efficiency audits for SMEs in Aguascalientes, Mexico}. 
%----------------------------------------------------------------------------------------
%	Awards and Honors
%----------------------------------------------------------------------------------------
\section{Grants} 
\hangindent=0.7cm  Shotaro Nakamura (PI), Matthew Gibson, Fatiq Nadeem, Sanval Nasim, and Arman Rezaee (Co-PIs). \textit{Belief Formation, Signal Quality, and Information Sources: Experimental Evidence on Air Quality from Pakistan}, 2022. International Growth Centre (IGC) PAK-22039. GBP 20,000. 

\hangindent=0.7cm  Sanval Nasim (PI), Matthew Gibson, Shotaro Nakamura, and Arman Rezaee (Co-PIs). \textit{Belief Formation, Signal Quality, and Information Sources: Experimental Evidence on Air Quality from Pakistan}, 2021. International Growth Centre (IGC) PAK-21105. GBP 15,000. 

\hangindent=0.7cm Girija Bahety, Castro Gichuki, and Shotaro Nakamura \textit{Do Community Currencies Induce ``Social'' Transactions and Enterprise Development?}, 2021. Private Enterprise Development in Low-Income Countries (PEDL). GBP 4,000. 

\hangindent=0.7cm  Travel and Research Grants, Department of Economics, UC Davis,  \hfill 2018, 2021, 2022


\section{Conference Presentations}
The Yale Research Initiative on Innovation and Scale (Y-RISE) Conference  \hfill 2022 \\
The North East Universities Development Consortium (NEUDC), Yale \hfill 2022 \\
Conference on Digital Experimentation, MIT \hfill 2022 \\
Tokyo Labor Economics Workshop \hfill 2022 \\
Conference on Applied Development Economics, Lahore School of Economics \hfill 2022 \\
%Nordic Conference in Development Economics \\
%NOVAFRICA PhD Workshop on Experimental Development Economics  \\
The Advances with Field Experiments, University of Chicago \hfill 2022 

\section{Refereeing}
Journal of Environmental Economics and Management

\section{Additional Research Experiences}
Research Assistant, Prof. Arman Rezaee, UC Davis \hfill 2018-2019 \\
Research Assistant, Profs. Erich Muehlegger and David Rapson, UC Davis \hfill 2018-2019 \\
Research Assistant (full-time pre-doc), Prof. Nava Ashraf, HBS and LSE \hfill 2014-2015, 2016-2017 \\
Research Analyst, Harvard Graduate School of Education  \hfill  2013-2014 \\
Research Assistant, Profs. Bruce Sacerdote and Sandip Sukhtankar, Dartmouth College \hfill 2010-2013
%----------------------------------------------------------------------------------------
%	Awards and Honors
%----------------------------------------------------------------------------------------

\section{Awards and Honors} 
Bilinski Educational Foundation Dissertation Writing Fellowship, UC Davis   \hfill 2022-2023  \\
Dean's Distinguished Graduate Fellowship, UC Davis \hfill 2017-2022  \\
Dean's Summer Graduate Fellowship, UC Davis \hfill 2020 \\
Departmental Honors, Economics, Dartmouth College \hfill 2013 \\




%----------------------------------------------------------------------------------------
%	COMPUTER SKILLS SECTION
%----------------------------------------------------------------------------------------


\section{Software and Languages}
Stata, R, \LaTeX, SQL \\
English (fluent) Japanese (native) \\
French (intermediate), Portuguese (intermediate)
 
%----------------------------------------------------------------------------------------
% References
%----------------------------------------------------------------------------------------


\section{References}
\begin{multicols}{2}
	
	Prof. Arman Rezaee  (Chair)\\
	Assistant Professor of Economics \\
	University of California, Davis \\
	\href{mailto:}{abrezaee@ucdavis.edu}
	
	
	\vfill\columnbreak
	
	Prof. David Rapson  \\
	Professor of Economics \\
	University of California, Davis \\
	\href{mailto:}{dsrapson@ucdavis.edu}
	
\end{multicols}

Prof. Giovanni Peri  \\
Professor of Economics \\
University of California, Davis \\
\href{mailto:}{gperi@ucdavis.edu }

\section{Placement Director} 
Prof. Andr\'{e}s Carvajal, 	\href{mailto:}{acarvajal@ucdavis.edu}

%----------------------------------------------------------------------------------------

\end{resume} 
\end{document}